\section{Conclusions and Improvements}

After assigning five people some tasks to execute in our mock application and asking them to rate the visual design, we found that most tasks were completed with relative ease by our respondents. They were also mostly positive about the visual design of the app. However, there were problems with the logic behind the buttons, windows and their placement. The most notable comments were about the admin overview being counter-intuitive and visually cluttered

We will work on making the admin page more intuitive, by making the page less crowded. This means taking admin features like editing a board away from the admin page and into the board view. This way an admin would be able to make changes, like changing the password, while on that board or from a page linked from that board rather than going to the control panel and having to fill in the board id of the board they want to edit. 

In our current mock, the “change colour” button is in line with and the same size as the save and delete buttons. Therefore, we plan on making the colour edit buttons consistent between tags and cards as well as changing their position and style to blend in less with the delete and save options. It will be moved up and get some colour itself so it stands out some more. Furthermore, after picking a colour for a tag the user should be sent back to the tag customization rather than the card customization page. On top of that, we will add more colour options, possibly by allowing our users to pick any hex value rather than limiting them to seven preselected colours. This will help with both making the boards look more like what the user wants and giving the option for power users with lots of tags to visually separate them better.

Currently, on the board overview the buttons for going back to picking a server and for going to the admin overview are both much bigger than the “join” button for joining a board by its id, while the joining of a new board is a more common task. We will make these buttons smaller and move them to the top left, moving the join by id section to the right. This makes more sense because the picking of a different server is the page you’ve just come from, and going back is usually in the top left of a page.

Overall, the expert's evaluation was successful in giving us a good overview of the users’ experience, what issues need to be addressed, and what changes need to be made in future iterations.
